Continuous gravitational waves in the lab: recovering audio signals with a table-top optical microphone

### 2021-05-04 paper/ifo-wanderingTone.tex
working on adding suggested references and response

The methods used here are directly inspired by LIGO-Virgo continuous wave searches. 
For further details on these methods see Refs.~\cite{SuvorovaEtAl:2016,SuvorovaEtAl:2017} and for searches performed using them see Refs.\cite{ScoX1O2Viterbi:2019, ScoX1ViterbiO1:2017, MillhouseStrangMelatos:2020, JonesSun:2020, MiddletonEtAlO2LMXBs:2020, PostMergerRemnantSearch:2019, SunEtAlSNR:2018, viterbi_application}. \han{check for new papers - add Deeksha's paper}

>>>>

The methods used here are  inspired by LIGO-Virgo continuous wave searches. 
For further details on these methods see Refs.~\cite{SuvorovaEtAl:2016,SuvorovaEtAl:2017} and for searches performed using them see Refs.\cite{ScoX1O2Viterbi:2019, ScoX1ViterbiO1:2017, MillhouseStrangMelatos:2020, JonesSun:2020, MiddletonEtAlO2LMXBs:2020, PostMergerRemnantSearch:2019, SunEtAlSNR:2018, viterbi_application}. \han{check for new papers - add Deeksha's paper}
For other continuous wave search analyses not discussed here, see for example Refs.\han{todo}\cite{} and for further information on searching for transient gravitational wave signals, see for example Refs.~\cite{MillhouseEtAl:2018, Mohanty:2017, AddessoEtAl:2016, ThraneCoughlin:2014, ThraneEtAl:2011, CandesEtAl:2008, ChassandeMottinArchana:2006, AndersonBalasubramanian:1999}.
